---
title: "Week 8, Day 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# Recall that Enos (2014) actually looks at a measure of change in attitude
# toward immigration, rather than simply at the ending attitude. Let's create
# such a variable and try to model it.

week_8 <- trains %>% 
  mutate(att_chg = att_end - att_start) %>% 
  select(att_chg, gender, party, treatment, liberal)
  
```

Weeks 7, 8 and 9 are the core of the class. We have a question. We have some data. How should we use the data to answer the question? Using Wisdom, we first decide if the question and the data are "close enough" that we can consider them to both be part of the same population. With Justice, we create a mathematical model which describes the connection between the outcome we want to explain/understand and the covariates which might be connected to it. Courage takes us from mathematics to code, creating a model, including posterior distributions for all its parameters. The last step is to use that model to answer the question with which we started, with Temperance.




## Scene 1

**Prompt:** Let's estimate and interpret three models. In each case, `att_chg` is the outcome variable, the thing we are trying to understand and explain. Use `stan_glm()` to create and print a model with `att_chg` (the dependent or outcome variable) as a function of the indicated independent (or predictor) variable. Do not use an intercept. In each case, write three sentences of interpretation, with a special focus on whether the model is predictive or causal. For causal models, indicate how you might estimate the causal effect.

* `att_chg` as a function of `gender`
```{r}
fit_model <- stan_glm(data = week_8,
                      family = gaussian(),
                      att_chg ~ gender - 1,
                      refresh = 0)

# You need to have a independent variable that you can change. You cannot manipulate gender, and can merely observe it and predict its effect on attention change. Predictive because we weren't randomly assining gender.
```


* `att_chg` as a function of `liberal`
```{r}
fit_model_1 <- stan_glm(data = week_8,
                      family = gaussian(),
                      att_chg ~ liberal - 1,
                      refresh = 0)
```


* `att_chg` as a function of `treatment`
```{r}
fit_model_2 <- stan_glm(data = week_8,
                      family = gaussian(),
                      att_chg ~ treatment - 1,
                      refresh = 0)

# This is a causal model because you can change and impact the independent variable.


```





## Scene 2

**Prompt:** For the model with `att_chg` as a function of `treatment`, create posterior probability densities for the two important parameters. Write a paragraph interpreting the meaning of those posteriors. 


```{r}
fit_model_2 %>%
  as_tibble() %>%
  rename(Treated = treatmentTreated,
         Control = treatmentControl) %>%
  pivot_longer(cols = -sigma,
               names_to = "treatment",
               values_to = "attitude_change") %>%
  select(- sigma) %>%
  ggplot(aes(x = attitude_change, fill = treatment)) +
  geom_density() 
  #scale_y_continuous(labels = scales::percent_format()) 

## Using y = afterstat works here (it would work for discrete values for geom_histogram + geom_density); after_stat(count/sum(count)) is usually used with histograms and density
## do we use the afterstat and normalize on the geomdensity
# the height of the geom_density are proportionate to the probabilities
# Can rely on a histogram to plot the posterior probability distribution (density and probability are different things that are proportional)
# a histogram has a finite number of bins; wheras a density plot has an infinite number of values on the x axis
## Why and when do we use the scale_y_continuous?
```


## Scene 3

**Prompt:** Create a plot of the the posterior for the average treatment effect. Write a paragraph interpreting the plot.


```{r}
fit_model_2 %>%
  as_tibble() %>%
  rename(Treated = treatmentTreated,
         Control = treatmentControl) %>%
  mutate(ate = Treated - Control) %>%
  ggplot(aes(x = ate)) +
  geom_histogram(aes(y = after_stat(count/sum(count)), fill = after_stat(count)), 
                 bins = 60) +
  scale_fill_gradient(low="blue", high="red")

```

